Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-24 ijar-npb-ms.tex
Table with surv. sign. for bridge system

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably taken as
$\vec{t}^1 = (2.2, 2.4, 2.6, 2.8)$ and $\vec{t}^2 = (3.2, 3.4, 3.6, 3.8)$, respectively.

\begin{table}
\centering
\begin{tabular}{crrrrr}
\toprule
$t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
\midrule
$\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250 \\
\bottomrule
\end{tabular}
\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system.}
\label{tab:bridge-T3prior}
\end{table}

>>>>

As a toy example, consider a `bridge' type system layout with three types of components T1, T2 and T3,
as depicted in Figure~\ref{fig:bridge-layout}.
The survival signature for this system is given in Table~\ref{tab:bridge-survsign}.
All rows with T3 $=0$ have been omitted; without T3, the system cannot function, thus $\Phi = 0$.
\begin{table}
\centering
\begin{tabular}{ccclccccl}
  \toprule
T1 & T2 & T3 & $\Phi$ & \quad & T1 & T2 & T3 & $\Phi$\\ 
  \midrule
0 & 0 & 1 & 0    & & 0 & 1 & 1 & 0 \\ 
1 & 0 & 1 & 0    & & 1 & 1 & 1 & 0 \\ 
2 & 0 & 1 & 0.33 & & 2 & 1 & 1 & 0.67 \\ 
3 & 0 & 1 & 1    & & 3 & 1 & 1 & 1 \\ 
4 & 0 & 1 & 1    & & 4 & 1 & 1 & 1 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature for the bridge system from Figure~\ref{fig:bridge-layout},
omitting all rows with T3 $=0$, since $\Phi=0$ for these.}
\label{tab:bridge-survsign}
\end{table}
For component types T1 and T2, we consider a near-noninformative set of prior reliability functions.
For components of type T3, we consider an informative set of prior reliability functions
as given in Table~\ref{tab:bridge-T3prior}.
This set could result from eliciting prior functioning probabilities at times $0,1,2,3,4,5$ only,
and filling up the rest.
These prior assumptions, together with sets of posterior reliability functions
resulting from three different scenarios for test data for component type T3,
are illustrated in Figures~\ref{fig:bridge-fitting}, \ref{fig:bridge-early} and \ref{fig:bridge-late}; 
test data for components of type T1 and T2 are invariably taken as
$\vec{t}^1 = (2.2, 2.4, 2.6, 2.8)$ and $\vec{t}^2 = (3.2, 3.4, 3.6, 3.8)$, respectively.

\begin{table}
\centering
\begin{tabular}{crrrrr}
\toprule
$t$ & $[0,1)$ & $[1,2)$ & $[2,3)$ & $[3,4)$ & $[4,5)$ \\
\midrule
$\ytzl{3}$ & 0.625 & 0.375 & 0.250 & 0.125 & 0.010 \\
$\ytzu{3}$ & 0.999 & 0.875 & 0.500 & 0.375 & 0.250 \\
\bottomrule
\end{tabular}
\caption{Lower and upper prior functioning probability bounds for component type T3 in the `bridge' system example.}
\label{tab:bridge-T3prior}
\end{table}
